\section{Purpose}
The purpose of this project is to use our knowledge in programming and incorporate it with the medical data provided by the hospital, to help them analyze patterns. Through the patterns, we hope to find improvements that can be implemented to help them with health-related issues. How can we help the hospital with our knowledge?

We can help them by building a free-to-use website, which will contain multiple analyses from the data set. The analysis will be visualized on the website through different types of charts. The reason behind using charts is that according to \cite{pyvis} humans have it easier to understand and analyze data if it is presented in different graphs, colors, and sizes rather than plain text with simple words and numbers. What is the reason for analyzing this particular set of data?


\cite{medData} claims that in Sweden the drug-related mortality rate has increased dramatically and there is a major concern for the country. Therefore, the data provided comes from different drug-related addictions. As mentioned earlier, patterns will be analyzed and while analyzing the data, three research questions will be explored to help with the analysis. What are those questions?

The first question is what types of changes in the population characteristics cause people to fall into drug addictions. This question will look through changes such as age, gender, socioeconomic status, education level, and other demographic factors.

The second question is about associations with preventive measures, which will look through whether the action taken to put a stop to an addiction is related to other factors. For example, it will look at the attempts made to stop drug-related issues linked with drug-related deaths. 

The third question to take into consideration is variations across geographical areas and subpopulations. Let us start with the geographical part, meaning if the preferences of drug-related substances differ depending on where you live. In other words, do different regions or places have different preferences when it comes to drugs. While subpopulations are more about specific groups within a larger population. For example, different age groups or income levels. 
