\section{Timeline}
According to \cite{juCourse} the expected timeline for the project will be between January to May, unfortunately, no certain days have been set for the months provided. The project will be started in January, and a registration form needs to be filled regarding the project. Together with the form, a project description will be handed to the course examiner. As mentioned earlier in the report, a website needs to be built, and therefore multiple parts such as the user interface (UI), a sketch of the database, and what programming language to use need to be planned. The UI is a design of what the website would look like, and the sketch of an entity relationship diagram is necessary to understand the relationship between variables. The current plan is to use JavaScript for the charts but the framework for the front end has not been decided yet and therefore, the first week of the project will be used to have the bases ready.   

Then in February a “planning report” should be handed in. \cite{juCourse} states that the following parts should be included: problem definition (define the knowledge/research gap, identify practical aspects for the partner company, how theoretical \& practical aspects are linked), proper research questions, the proposed research approach (method) is relevant, the expected output or result is defined, the outlined schedule is realistic.


In April a halfway presentation will be presented, the presentation is about the progress made from January to April and according to \cite{juCourse} will contain the following parts: a description of the problem area, a summary of theoretical background, based on the literature review, purpose, and research questions, detailed description of chosen research method and motivation, theoretical framework, preliminary results (if available), problems and open questions to solve, next steps (in particular data gathering and analysis).




Lastly, in June a final presentation should be presented with the final version of the project, but two weeks before the presentation, a review version of the thesis report will be handed in. Then the supervisor will re-post the report to a group that will give us an opposition review.  When it comes to the presentation \cite{juCourse} states that the length of the presentation should be around 20 minutes and contain the following parts should be included: a description of the problem area, a summary of theoretical background, purpose, and research questions, a detailed description of the chosen method (including motivation and implementation), conduct of the research, results, and analysis, conclusions.
